Network Cascades

### 2016-08-25 paper/paper.tex
Clarify cascade condition

>>>>

That is, a successful cascade is only possible, if the graph's largest connected cluster of agents changes its state to $1$. This is only a necessary condition however: if the cascade condition is not fulfilled, a successful cascade is impossible, but a fulfilled cascade condition does not guarantee a successful cascade.
